cardinalR: Generating interesting high-dimensional data structures

### 2025-04-25 paper-cardinalR.Rmd
Started working on clustring example

```{r load-libraries}
library(cardinalR)
library(tidyverse)
library(kableExtra)
library(geozoo)
library(patchwork)
```

@@

>>>>

```{r load-libraries}
library(cardinalR)
library(tidyverse)
library(kableExtra)
library(geozoo)
library(patchwork)
library(GGally)
library(ggdendro)
library(mulgar)
```

@@

```{r}
ggscatmat(three_clusts[, -8]) + 
  theme_minimal() +
  xlab("") + ylab("")
```

```{r}
p_dist <- dist(three_clusts[, -8])
p_hcw <- hclust(p_dist, method="ward.D2")
p_hcs <- hclust(p_dist, method="single")

p_clw <- three_clusts[, -8] |> 
  mutate(cl = factor(cutree(p_hcw, 3))) |>
  as.data.frame()
p_cls <- three_clusts[, -8] |> 
  mutate(cl = factor(cutree(p_hcs, 3))) |>
  as.data.frame()

p_w_hfly <- mulgar::hierfly(p_clw, p_hcw, scale=FALSE)
p_s_hfly <- mulgar::hierfly(p_cls, p_hcs, scale=FALSE)
```

```{r}
# Generate the dendrograms in 2D
p_hcw_dd <- ggdendro::dendro_data(p_hcw)
pw_dd <- ggplot() +
  geom_segment(data=p_hcw_dd$segments, 
               aes(x = x, y = y, 
                   xend = xend, yend = yend)) + 
  geom_point(data=p_hcw_dd$labels, aes(x=x, y=y),
             alpha=0.8) +
  theme_dendro()

p_hcs_dd <- ggdendro::dendro_data(p_hcs)
ps_dd <- ggplot() +
  geom_segment(data=p_hcs_dd$segments, 
               aes(x = x, y = y, 
                   xend = xend, yend = yend)) + 
  geom_point(data=p_hcs_dd$labels, aes(x=x, y=y),
             alpha=0.8) +
  theme_dendro()
```
